\vspace{-2cm} Government Websites As Data: \\ A methodological pipeline with application to the websites of municipalities in the United States

### 2021-09-27 paper/manuscript_jitp_rr2.tex
typo

The manual approach is expensive, and is also subject to human error, judgement calls, and inter-coder reliability problems. Furthermore, researchers looking only for specific pieces of information are bound to miss a lot of content that doesn't fall within their pre-defined objectives. Moreover, city websites often contain thousands of pages \citep{Urban2002}\footnote{\cite{Urban2002} relies on a webcrawler to measure how many pages each city website is comprised of, which is also the first step of \texttt{wget}. In this way, his research is a precursor to our own, albeit without the actual analysis of each page.}, so even projects with substantial human resources might struggle to provide a complete understanding of individual websites. \hl{It is now standard practice to combine human coding with machine-learning based content classification} \citep[e.g., ][]{sebHok2021multiclass,fowler2021political}. \hl{If researchers had access to machine-readable content associated with government websites, a smaller quantity of human coding could be used to develop machine classifiers for attributes of interest, which could in tern be used to classify much larger sets of websites than is possible to do with human-only coding methods.} Unfortunately, scrapers conventionally used in the social sciences \citep[e.g.,][]{cryer2019navigating} rely on extracting text through specific HTML tags, which makes it difficult to apply to a large number of websites, because the process needs to be adjusted for each site. By contrast, the only input our pipeline requires is the site URL.

>>>>

The manual approach is expensive, and is also subject to human error, judgement calls, and inter-coder reliability problems. Furthermore, researchers looking only for specific pieces of information are bound to miss a lot of content that doesn't fall within their pre-defined objectives. Moreover, city websites often contain thousands of pages \citep{Urban2002}\footnote{\cite{Urban2002} relies on a webcrawler to measure how many pages each city website is comprised of, which is also the first step of \texttt{wget}. In this way, his research is a precursor to our own, albeit without the actual analysis of each page.}, so even projects with substantial human resources might struggle to provide a complete understanding of individual websites. \hl{It is now standard practice to combine human coding with machine-learning based content classification} \citep[e.g., ][]{sebHok2021multiclass,fowler2021political}. \hl{If researchers had access to machine-readable content associated with government websites, a smaller quantity of human coding could be used to develop machine classifiers for attributes of interest, which could in turn be used to classify much larger sets of websites than is possible to do with human-only coding methods.} Unfortunately, scrapers conventionally used in the social sciences \citep[e.g.,][]{cryer2019navigating} rely on extracting text through specific HTML tags, which makes it difficult to apply to a large number of websites, because the process needs to be adjusted for each site. By contrast, the only input our pipeline requires is the site URL.
